Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-03 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

```{r data, include=FALSE}
#Data Collection
game_log_2020 <- read.csv(file="Game_Log_2020.csv", header=TRUE)
game_log_2017_2019 <- read.csv(file="2017-2019_game_data.csv", header=TRUE)

>>>>

```{r data, include=FALSE}
#Data Collection
game_log_2020 <- read.csv(file="../data/Game_Log_2020.csv", header=TRUE)
game_log_2017_2019 <- read.csv(file="../data/2017-2019_game_data.csv", header=TRUE)
